Automating Verification of MPC Security

### 2023-06-03 popl24/metalang.tex
checkpoint

$$
\begin{array}{rcl@{\hspace{8mm}}r}
b &\in& \{ \etrue, \efalse \} \\
w &\in& \mathrm{String} \\ 
\cid &\in& \mathrm{Clients} \qquad  (\mathrm{Clients} \subset \mathbb{N} \text{\ in\ this\ presentation})\\[2mm]
\bop &\in& \{ \eand, \eor, \exor \} \\[2mm]
\be &::=& b \mid \flip{\cid}{w} \mid \secret{\cid}{w} \mid \view{\cid}{w} \mid \oracle{w} \mid & \textit{boolean expressions}\\
& &  \enot\ \be \mid \be\ \bop\ \be \mid \OT{\be}{\be}{\be} \mid \select{\be}{\be}{\be} \\[2mm]
\instr &::=& \eassign{\view{\cid}{w}}{\be} \mid \eassign{\view{\cid}{w}}{\OT{\be}{\be}{\be}} & \textit{view assignments} \\[2mm]
\prog &::=& \instr \mid \instr; \prog & \textit{protocols}
\end{array}
$$

@@

$$
\begin{array}{rcl@{\hspace{8mm}}r}
b &\in& \{ \etrue, \efalse \} \\
w &\in& \mathrm{String} \\ 
\flab &\in& \mathrm{Field}\\
s,x &\in& \mathrm{EVar}\\
f &\in& \mathrm{FName}\\
\cid &\in& \mathrm{Clients} \qquad  \mathrm{Clients} = \mathbb{N} \text{\ is\ OK}\\
\alpha,\beta &\in& \mathrm{DVar} \qquad \ttt{'a}, \ttt{'b} \text{\ etc.\ is\ OK}\\[5mm]
% \str &::=& w \ \mid \ s \ \mid \ \str||\str & \textit{string terms}\\[2mm]
e &::=& b \mid \flip{e}{e} \mid \secret{e}{e} \mid \view{e}{e} \mid \oracle{e} \mid \enot\ e \mid e\ \eand\ e \mid e\ \exor\ e \mid & \textit{expressions}\\[1mm]
& & \OT{e}{e}{e} \mid \select{e}{e}{e} \mid 
\send{\view{e}{e}}{e} \mid e;e \mid \elet{x}{e}{e} \mid\\[1mm]
& & x \mid f(e,\ldots,e) \mid \{ \flab = e; \ldots; \flab = e \}
\mid e.\flab \mid e\ttt{||}e \mid (e) \\[2mm]
v &::=& w \mid b \mid \cid \mid \{ \flab = v;\ldots;\flab = v \} 
 \mid (\,) & \textit{values}
\end{array}
$$

The syntax of functions is as follows. We require type annotations 
formal parameters. These types support the categories of values. 
The full type syntax is richer than the syntax of type annotations, 
as we show below, but a restricted language here simplifies type 
checking.
$$
\begin{array}{rcl@{\hspace{15mm}}r}
{fn} &::=& f(x : \srct,\ldots,x : \srct) \{ e \} & \textit{functions}\\[3mm]
\srct &::=& \cidty{x} \mid \stringty{x} \mid \jpdty{\alpha}{\alpha} \mid
    \{ \flab : \srct;\ldots;\flab : \srct \} 
& \textit{annotated types} \end{array}
$$

\begin{definition}
A \emph{codebase} $\codebase$ is a list of function 
declarations. We write $ \codebase(f) = x_1,\ldots,x_n,\ e$
iff $f(x : \srct,\ldots,x : \srct) \{ e \} \in \codebase$.
A \emph{program}, aka \emph{protocol} $\prot$ is a pair of a 
codebase and expression $\codebase, e$. We may omit
$\codebase$ if it is clear from context.  
\end{definition}

>>>>

$$
\begin{array}{rcl@{\hspace{8mm}}r}
b &\in& \{ \etrue, \efalse \} \\
w &\in& \mathrm{String} \\ 
\cid &\in& \mathrm{Clients} \qquad  (\mathrm{Clients} \subset \mathbb{N} \text{\ in\ this\ presentation})\\[2mm]
\bop &\in& \{ \eand, \eor, \exor \} \\[2mm]
\be &::=& b \mid \flip{\cid}{w} \mid \secret{\cid}{w} \mid \view{\cid}{w} \mid \oracle{w} \mid & \textit{boolean expressions}\\
& &  \enot\ \be \mid \be\ \bop\ \be \mid \select{\be}{\be}{\be} \\[2mm]
\instr &::=& \eassign{\view{\cid}{w}}{\be} \mid \eassign{\view{\cid}{w}}{\OT{\be}{\be}{\be}} & \textit{view assignments} \\[2mm]
\prog &::=& \instr \mid \instr; \prog & \textit{protocols}
\end{array}
$$

@@

$$
\begin{array}{rcl@{\hspace{8mm}}r}
\flab &\in& \mathrm{Field}\\
x &\in& \mathrm{EVar}\\
f &\in& \mathrm{FName}\\[2mm]
e &::=& b \mid \flip{e}{e} \mid \secret{e}{e} \mid \view{e}{e} \mid \oracle{e} \mid \enot\ e \mid e\ \eand\ e \mid e\ \exor\ e \mid & \textit{expressions}\\[0mm]
& & \select{e}{e}{e} \mid 
\send{\view{e}{e}}{e} \mid \send{\view{e}{e}}{\OT{e}{e}{e}} \mid e;e \mid \\[0mm]
& & x \mid \elet{x}{e}{e} \mid f(e,\ldots,e) \mid \{ \flab = e; \ldots; \flab = e \}
\mid e.\flab \mid e\ttt{||}e \mid (e) \\[2mm]
v &::=& w \mid b \mid \cid \mid \{ \flab = v;\ldots;\flab = v \} 
\mid (\,) & \textit{values}\\[2mm]
{fn} &::=& f(x,\ldots,x) \{ e \} & \textit{functions}
\end{array}
$$

\begin{definition}
A \emph{codebase} $\codebase$ is a list of function 
declarations. We write $ \codebase(f) = x_1,\ldots,x_n,\ e$
iff $f(x_1,\ldots,x_n) \{ e \} \in \codebase$.
A \emph{metaprogram}, aka \emph{mataprotocol} is a pair of a 
codebase and expression $\codebase, e$. We may omit
$\codebase$ if it is clear from context.  
\end{definition}

$$
\begin{array}{rcl@{\hspace{3mm}}r}
E &::=& [\,] \mid \enot\ E \mid E\ \bop\ e \mid v\ \bop\ E \mid & \textit{evaluation contexts}\\[1mm]
& & \flip{E}{e} \mid \secret{E}{e} \mid \view{E}{e} \mid \oracle{E} \mid  \\[1mm]
& & \flip{\cid}{E} \mid \secret{\cid}{E} \mid \view{\cid}{E} \mid \send{E}{e} \mid \send{\view{\cid}{w}}{E}\\[1mm]
& & \OT{E}{e}{e} \mid \OT{v}{E}{e} \mid \OT{v}{v}{E} \mid\\[1mm]
& & \select{E}{e}{e} \mid \select{v}{E}{e} \mid \select{v}{v}{E} \mid\\[1mm]
& & \elet{x}{E}{e} \mid f(v,\ldots,v,E,e,\ldots,e) \mid \\[1mm]
& & \{ \flab = v;\ldots;\flab = v;\flab = E;\flab = e;\ldots;\flab = e \} \mid E.\flab \mid E\ttt{||}e \mid v \ttt{||}E
\end{array}
$$

$$
\begin{array}{rcl@{\hspace{10mm}}r}
\config{\prog}{\elet{x}{v}{e}} &\redx& \config{\prog}{e[v/x]}\\
\config{\prog}{f(v_1,...,v_n)} &\redx&
\config{\prog}{e[v_1/x_1,\ldots,v_n/x_n]} & 
 \codebase(f) = x_1,\ldots,x_n,\ e\\
\config{\prog}{\{\ldots; \flab = v; \ldots\}.\flab} &\redx&
 \config{\prog}{v}\\
 \config{\prog}{w_1\ttt{||}w_2} &\redx& \config{\prog}{w_1w_2}\\
 \config{\prog}{v;e} &\redx& \config{\prog}{e}\\
\config{\prog}{\instr} &\redx& \config{\prog;\instr}{()}\\
\config{\prog}{E[e]} &\redx& \config{\prog'}{E[e']} & \text{if}\ \config{\prog}{e} \redx \config{\prog'}{e'} 
\end{array}
$$
